---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# getFertilizer 

![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/getFertilizer)
[![Travis-CI Build Status](https://travis-ci.org/wenlong-liu/getFertilizer.svg?branch=master)](https://travis-ci.org/wenlong-liu/getFertilizer)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/wenlong-liu/getFertilizer?branch=master&svg=true)](https://ci.appveyor.com/project/wenlong-liu/getFertilizer)
[![](https://cranlogs.r-pkg.org/badges/getFertilizer)](https://cran.r-project.org/package=getFertilizer)
[![metacran downloads](http://cranlogs.r-pkg.org/badges/grand-total/getFertilizer?color=ff69b4)](https://cran.r-project.org/package=getFertilizer)

## Retrieve, Summarize and Visualize the Fertilizer Data in USA
Provides a user-friendly API to further dig in County-Level Fertilizer data in USA, provided by USGS. 
             
## Installation

This package can be installed via github using devtools.

```{r, eval=FALSE}
# install.package("devtools")   #In case you have not installed it.
devtools::install_github("wenlong-liu/getFertilizer")
```

## Quick Start
### Import data and libraries
```{r data, message=FALSE}
require(usfertilizer)
require(getFertilizer)
require(dplyr)
require(ggplot2)
data("us_fertilizer_county")
```

### Retrieve fertilizer data

```{r}
Year <-  2008
Nutrient <- "N"
Input_Type <- "fertilizer"

# retrieve data.
plot_data <- get_data(data = us_fertilizer_county, years = Year, nutrient = Nutrient, 
                      input_type = Input_Type,  combine_state_county = TRUE)
head(plot_data)
```

### Summarize and plot data. 

#### Example 1: Find out the top 10 counties with most nitrogen appliation in 2008.

```{r}
# plot the top 10 nitrogen application in year 2008.
plot <- plot_data %>% 
  top_n(10, Quantity) %>%
  ggplot(aes(x=reorder(County, Quantity), Quantity, fill = Quantity))+
  scale_fill_gradient(low = "blue", high = "darkblue")+
  geom_col()+
  ggtitle(paste("Top 10 counties with most N fertilizer application in the year of", Year)) + 
  scale_y_continuous(name = "Nitrogen from commecial fertilization (kg)")+
  scale_x_discrete(name = "Counties")+
  coord_flip()+
  theme_bw()
plot
```

### Examples 2: Visualize the fertilizer data in US maps.

```{r}
Year = 2001
Nutrient = "N"
Farm_Type = "farm"
Input_Type = "fertilizer"
level  = "county"

# draw the map
us_plot <- map_us_fertilizer(data = us_fertilizer_county, Year = Year, Nutrient = Nutrient,
                             Farm_Type = Farm_Type, Input_Type = Input_Type,
                             viridis_palette = "inferno", level = level)
us_plot <- us_plot +
  ggtitle(paste(Nutrient, " from ", Input_Type, " input to ", Farm_Type, " in the year of ",Year,
                     " at ", level, " level",sep = ""))+
  labs(caption = "Data source: United State Geography Service (USGS)")
us_plot
```

As the map is a ggplot2 object, users can play with it as normal ggplot2 graphs.  Such we can change the projection system of the map to "albers" projection.

```{r projection, message=FALSE}
us_plot +
  coord_map("albers",lat0=39, lat1=45)
```

The map can also be drawn at state level.  The built-in function will automatically sum up all the data with the corresponding states.
```{r}
Year = 2007
Nutrient = "P"
Farm_Type = "nonfarm"
Input_Type = "fertilizer"
level  = "state"

# draw the map
us_plot <- map_us_fertilizer(data = us_fertilizer_county, Year = Year, Nutrient = Nutrient,
                             Farm_Type = Farm_Type, Input_Type = Input_Type,
                             viridis_palette = "inferno", level = level)
us_plot <- us_plot +
  ggtitle(paste(Nutrient, " from ", Input_Type, " input to ", Farm_Type, " in the year of ",Year,
                     " at ", level, " level",sep = ""))+
  labs(caption = "Data source: United State Geography Service (USGS)")
us_plot
```

For more details about mapping fertilizer data, please see this [vignettes](https://wenlong-liu.github.io/getFertilizer/articles/US_maps.html)

### Generate summaries plots. 

(under development on July 10, 2018)

## Comments and Questions

If you have any problems or questions, feel free to open an issue [here](https://github.com/wenlong-liu/getFertilizer/issues).

## Lisence

[GPL](https://github.com/wenlong-liu/getFertilizer/blob/master/LICENSE)

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/wenlong-liu/getFertilizer/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.
