---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# getFertilizer 

![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/getFertilizer)
[![Travis-CI Build Status](https://travis-ci.org/wenlong-liu/getFertilizer.svg?branch=master)](https://travis-ci.org/wenlong-liu/getFertilizer)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/wenlong-liu/getFertilizer?branch=master&svg=true)](https://ci.appveyor.com/project/wenlong-liu/getFertilizer)
[![](https://cranlogs.r-pkg.org/badges/getFertilizer)](https://cran.r-project.org/package=getFertilizer)
[![metacran downloads](http://cranlogs.r-pkg.org/badges/grand-total/getFertilizer?color=ff69b4)](https://cran.r-project.org/package=getFertilizer)

## Retrieve, Summarize and Visualize the Fertilizer Data in USA
Provides a user-friendly API to further dig in County-Level Fertilizer data in USA, provided by USGS. 
             
## Installation

This package can be installed via github using devtools.

```{r, eval=FALSE}
# install.package("devtools")   #In case you have not installed it.
devtools::install_github("wenlong-liu/getFertilizer")
```

## Quick Start



## Comments and Questions

If you have any problems or questions, feel free to open an issue [here](https://github.com/wenlong-liu/getFertilizer/issues).

## Lisence

[GPL](https://github.com/wenlong-liu/getFertilizer/blob/master/LICENSE)

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/wenlong-liu/getFertilizer/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.
