---
title: "Get started with getFertilizer"
author: "Wenlong Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with getFertilizer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Retrieve, Summarize and Visualize the Fertilizer Data in USA

Provides a user-friendly API to further dig in County-Level Fertilizer data in USA, provided by USGS. 
             
## Installation

This package can be installed via CRAN.

```{r, eval=FALSE}
# Not available yet.
install.packages("getFertilizer")
```


## Quick Start
### Import data and libraries

```{r data, message=FALSE}
require(usfertilizer)
require(getFertilizer)
require(dplyr)
require(ggplot2)
data("us_fertilizer_county")
```

### Retrieve fertilizer data

```{r}
Year <-  2008
Nutrient <- "N"
Input_Type <- "fertilizer"

# retrieve data.
plot_data <- get_data(data = us_fertilizer_county, years = Year, nutrient = Nutrient, 
                      input_type = Input_Type,  combine_state_county = TRUE)
head(plot_data)
```

### Summarize and plot data. 

#### Example 1: Find out the top 10 counties with most nitrogen appliation in 2008.

```{r}
# plot the top 10 nitrogen application in year 2008.
plot <- plot_data %>% 
  top_n(10, Quantity) %>%
  ggplot(aes(x=reorder(County, Quantity), Quantity, fill = Quantity))+
  scale_fill_gradient(low = "blue", high = "darkblue")+
  geom_col()+
  ggtitle(paste("Top 10 counties with most N fertilizer application in the year of", Year)) + 
  scale_y_continuous(name = "Nitrogen from commecial fertilization (kg)")+
  scale_x_discrete(name = "Counties")+
  coord_flip()+
  theme_bw()
plot
```

### Examples 2: Visualize the fertilizer data in US maps.

```{r}
Year = 2001
Nutrient = "N"
Farm_Type = "farm"
Input_Type = "fertilizer"
level  = "county" 

# draw the map
us_plot <- map_us_fertilizer(data = us_fertilizer_county, Year = Year, Nutrient = Nutrient,
                             Farm_Type = Farm_Type, Input_Type = Input_Type, 
                             viridis_palette = "inferno", level = level) 
us_plot
```

As the maps are actually ggplot2 objects, all the common API for ggplot2 can be used here. We can also add a title for the map to make it more informative.
 
```{r}
us_plot +
  ggtitle(paste(Nutrient,  " from ", Input_Type, " input to ", Farm_Type, " in the year of ",Year,
                     " at ", level, " level",sep = ""))
```


For more details about mapping fertilizer data, please see this [vignettes](https://wenlong-liu.github.io/getFertilizer/articles/US_maps.html)

### Visualize the fertilizer data for different states.


### Generate summaries plots. 

(under development on July 10, 2018)

## Comments and Questions

If you have any problems or questions, feel free to open an issue [here](https://github.com/wenlong-liu/getFertilizer/issues).

## Lisence

[GPL](https://github.com/wenlong-liu/getFertilizer/blob/master/LICENSE)
